Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects

### 2024-05-08 paper.tex
Remove erroneous information about speedup

\section{Summary}
In this paper, we have considered the problem of computing n-point correlation
functions, namely $S_n, C_n, F_{s...s}$ and $F_{s...v}$, for which
computationally efficient algorithms can be developed (including computations on
GPU). For $n=3$ we have developed code in Julia language to compute $S_3, C_3,
F_{sss}, F_{ssv}$ and $F_{svv}$ with a right-angle triangle pattern. This
pattern is much easier to vectorize and parallelize compared to previously used
random triangle or spider-web sampling patterns. Moreover, it allows to easily
implement computations of directional 3-point CFs. The execution times for the
same number of sample are orders of magnitude lower than existing published
counterparts. We showed that the volume of data produced get unwieldy very
easily, especially if computations are performed in frequency domain. For these
reasons until information content of different sets of correlation functions
with different "n-pointness" is not known, it is seemingly no much reason to
increase the number of points. Nonetheless, developed algorithms and code are
universal enough to be easily extendable to any $n$ (with increasing
computational and RAM burden). All results are available as part of open source
package \code{CorrelationFunctions.jl}, developed by our group and freely
available to the public with numerous Jupiter notebooks showing examples of
applications to assess 3-point correlation functions for 2D and 3D images.

>>>>

\section{Summary}
In this paper, we have considered the problem of computing n-point correlation
functions, namely $S_n, C_n, F_{s...s}$ and $F_{s...v}$, for which
computationally efficient algorithms can be developed (including computations on
GPU). For $n=3$ we have developed code in Julia language to compute $S_3, C_3,
F_{sss}, F_{ssv}$ and $F_{svv}$ in an arbitrary set of points. We also provide a
function which generates a right-angle triangle pattern. Computations are easily
vectorized and utilize the power of modern CPU and GPU architectures. The
execution times for the same number of sample are orders of magnitude lower than
existing published counterparts. We showed that the volume of data produced get
unwieldy very easily, especially if computations are performed in frequency
domain. For these reasons until information content of different sets of
correlation functions with different "n-pointness" is not known, it is seemingly
no much reason to increase the number of points. Nonetheless, developed
algorithms and code are universal enough to be easily extendable to any $n$
(with increasing computational and RAM burden). All results are available as
part of open source package \code{CorrelationFunctions.jl}, developed by our
group and freely available to the public with numerous Jupiter notebooks showing
examples of applications to assess 3-point correlation functions for 2D and 3D
images.
